Ethereum: Un Registro Generico delle Transazioni Sicuro e Decentralizzato \\ {\smaller \textbf{Final Draft - UNDER REVIEW}}

### 2016-01-15 Paper.tex
Update Paper.tex

Ethereum è un progetto che tenta di costuire una tecnologia generalizzata; dove tutte le idee basate sulla macchina di transizione di stato possono essere costruite. Moreover it aims to provide to the end-developer a tightly integrated end-to-end system for building software on a hitherto unexplored compute paradigm in the mainstream: a trustful object messaging compute framework.

@@

There are many goals of this project; one key goal is to facilitate transactions between consenting individuals who would otherwise have no means to trust one another. This may be due to geographical separation, interfacing difficulty, or perhaps the incompatibility, incompetence, unwillingness, expense, uncertainty, inconvenience or corruption of existing legal systems. By specifying a state-change system through a rich and unambiguous language, and furthermore architecting a system such that we can reasonably expect that an agreement will be thus enforced autonomously, we can provide a means to this end.

Dealings in this proposed system would have several attributes not often found in the real world. The incorruptibility of judgement, often difficult to find, comes naturally from a disinterested algorithmic interpreter. Transparency, or being able to see exactly how a state or judgement came about through the transaction log and rules or instructional codes, never happens perfectly in human-based systems since natural language is necessarily vague, information is often lacking, and plain old prejudices are difficult to shake.

>>>>

Ethereum è un progetto che tenta di costuire una tecnologia generalizzata; dove tutte le idee basate sulla macchina di transizione di stato possono essere costruite. Inoltre esso mira a fornire allo svilupattore finale un sistema end-to-end molto integrato per la costruzione di software su un paridgma di calcolo nel finora inesplorato nel mainstream: un framework computazionario di fiducia che scambia messaggi.

@@

Molti sono gli obiettivi di questo progetto; il principale è quello di facilitare le transazioni consentendo agli individui, che altrimenti non avrebbero mezzi, di fidarsi tra di loro. Ciò potrebbe derivare dalla distanza geografica, la difficoltà ad incontrarsi, o probabilmente all'incompatibilità, incapacità, riluttanza, costi, incertezza, non convenienza o la corruzione dei sistemi legali esistenti. Fornendo le specifiche per lo sviluppo di un sistema di cambio di stato attraverso un linguaggio ricco e chiaro ed architettando un sistema come questo, possiamo ragionevolmente aspettarci che un accordo sarà ottemperato automaticamente, procurando un mezzo per tale fine.

Conseguentemente il sopracitato sistema avrebbe diversi attributi non spesso rinvenibili nel mondo reale. L'incorrutibilità di un giudizio, spesso difficile da trovare, perviene naturalmente da un interprete algoritmico disinteressato. La trasparenza QUI Transparency, or being able to see exactly how a state or judgement came about through the transaction log and rules or instructional codes, never happens perfectly in human-based systems since natural language is necessarily vague, information is often lacking, and plain old prejudices are difficult to shake.
